---
title: "BDA hw2"
author: "2020311198 Dongook Son"
output: pdf_document
---
```{r, include=FALSE}
library(ggplot2)
```

## (2) Probability of a girl birth given placenta previa

We can set up the variable in the following way.  
$$
\begin{split}
y : \text{event of female birth; 437}  \\ 
n : \text{total number of births; 980} \\ 
\theta : \text{probability of placenta previa} 
\end{split}
$$
Then we can construct a Binomial model to see whether the claim that the proportion of female births in the population of placenta previa is less than 0.485.  

### Prior : Uniform(0,1)

First, we can use a Uniform(0,1) non-informative prior for $\theta$. Since, Uniform(0,1) distribution is a special case of the Beta distribution($Beta(\alpha,\beta)$), we can directly derive the posterior distribution by conjugacy.  

$$
\begin{aligned}
\theta | y &\sim Beta(437+1, 980-437+1) \\ 
&\sim Beta(438, 544)
\end{aligned}
$$

The mean and variance of the posterior distribution can be derived mathematically.

$$
E[\theta | y] = \frac{438}{438 + 544} \approx 0.4460
$$

$$
Var(\theta | y) = \frac{438 * 544}{(438+544)^2(438+544+1)} \approx 0.0002513602 \approx 0.0159^2 
$$

The 95% credible interval can be computed in the following way.
```{r}
(lower_bound <- qbeta(0.025, 438, 544))
(upper_bound <- qbeta(1-0.025, 438, 544))
```


```{r, fig.width=5, fig.align='center'}
domain <- seq(0,1,0.001)
image <- dbeta(domain, 438, 544)
plot(domain, image, 
     main='Posterior distribution\nBeta(438,544)', 
     frame.plot = FALSE,
     type = 'l',
     )
polygon(c(domain[domain > lower_bound & domain < upper_bound], upper_bound, lower_bound), 
        c(image[domain > lower_bound & domain < upper_bound], 0, 0), 
        col = 'grey')
```

